Software architectures to integrate workflow engines in science gateways

### 2016-10-13 answers.tex
Still more answers to the reviewers

@@

@@

@@

>>>>

\begin{answer}
  The revised manuscript now adds examples for tight integration
  (Catania Science Gateway Framework) and workflow conversion
  (Tavaxy).
\end{answer}

@@

\begin{review}
  We agree with the reviewer that the Figures are difficult to
  understand, however, we think it is important that the original
  figures describing the system architectures are used. Indeed, a goal
  of the examples is to illustrate the matching between our
  architectures and the real system. As a compromise, we edited the
  original figures with red color, to indicate where the software
  components and interactions of our architectures fit. We hope the
  figures are easier to read now.
\end{review}

@@

\begin{answer}
We rephrased as follows:
\emph{The science gateway may also implement mechanisms to facilitate the handling of task
dependencies, for instance lists of tasks that must
be completed before a particular task can be executed.}
\end{answer}

@@

\begin{answer}
  We followed the recommendation of the reviewer and created a new
  Section 3 to present and discuss these examples. The caption of
  Figures 5 and 6 is still long though, because we think that the
  detailed references to the interaction numbers on the Figures should
  be part of them, so that the reader doesn't have to constantly
  navigate between the text and the Figures.
\end{answer}
